% Shalini_Gandhi.tex

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage{fullpage}
\usepackage{color}
\usepackage{pxfonts}
\usepackage{fancyhdr}
\usepackage{setspace}

\definecolor{mygrey}{gray}{0.80}
\textheight=8.8in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\textwidth}{0.9in}

\linespread{0.9}

\pagestyle{fancy}
\setlength{\headsep}{5pt}
\setlength{\headheight}{0.9in}
\fancyhead{}
\fancyhead[L]{\textbf{\Large Shalini Gandhi} \\ \textbf{\large LEED AP BD+C}}
\fancyhead[R]{1431 28th Street S Apt\#5 \\ Arlington, VA 22206 \\ +1 (425) 785 9240 \\ shalini.gandhi@gmail.com}
\fancyfoot{}
\renewcommand{\headrulewidth}{1pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{1.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\vspace{0.6in} \begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
\end{tabular*}}
%-----------------------------------------------------------

\begin{document}
%\resheading{Objective}
%  \begin{itemize}
%    \resitem{Seeking a full-time position to utilize my education, and gain work experience to broaden my practical knowledge of the construction profession.}
%  \end{itemize}

\resheading{Education}
\begin{itemize}
\item
  \ressubheading{University of Washington}{Seattle, WA, USA}{Master of Science in Construction Management}{Sep. 2008 - Dec. 2009}
\item
  \ressubheading{Manipal University}{Manipal, Karnataka, India}{Bachelor of Architecture}{Sep. 2002 - Nov. 2007}
\end{itemize}

\resheading{Skills}
\begin{itemize}
  \resitem{\textbf{Drawing and Modeling}: AutoCAD, Architectural Desktop/AutoCAD Architecture, AutoCAD 3D VIZ, 3DS Max, SketchUp}
  \resitem{\textbf{Building Information Modeling (BIM):} Autodesk Navisworks}
  \resitem{\textbf{Project Management:} Primavera, Microsoft Project}
  \resitem{\textbf{Applications:} Microsoft Office, Adobe Suite}
  \resitem{\textbf{Operating Systems:} Windows, Mac OS}
\end{itemize}

\resheading{Relevant Work Experience}
\begin{itemize}

\item
  \ressubheading{SIGAL Construction Corporation}{Arlington, VA, USA}{Assistant Project Manager and BIM Coordinator}{Aug. 2010 - Present}
  \begin{itemize}
    \resitem{Working on HSC Foundation, an office building worth \$9 million that involves a historic carriage house for restoration and is going to be LEED Gold.}
    \resitem{Coordinating all trades using Building Information Modeling (BIM) to ensure compliance with project schedules, budgets, and specifications.}
    \resitem{Running clash detection, and preparing schedules and estimates using BIM.}
    \resitem{Preparing presentation drawings and 3D models for various projects.}
    \resitem{Collecting and processing LEED documentation with subcontractors, architects, and engineers.}
    \resitem{Collecting and coordinating RFIs and Submittals to ensure compliance with project specification.}
    \resitem{Collecting and processing 2D and 3D drawings, contract documents, permits, and other documentation for design and construction coordination.}
    \resitem{Processing change order documentation and associated cost reports.}
    \resitem{Leading BIM coordination meetings.}
    \resitem{Responsible for project cost review, report, updates, and accounts.}
    \resitem{Involved with pre-construction services and value engineering.}
    \resitem{Involved in the bidding process of various projects.}
    \resitem{Coordinating project closeouts.}
  \end{itemize}
\item
  \ressubheading{Icon Development Group}{Algonquin, IL, USA}{Intern}{Apr. 2010 - Aug. 2010}
  \begin{itemize}
    \resitem{Preparing the scope of work for various residential construction projects.}
    \resitem{Assisting with the development of project budgets.}
    \resitem{Requesting and collecting proposals from subcontractors, and cross-checking them for accuracy.}
    \resitem{Obtaining information and approvals from clients and ensure conformance to the project schedule.}
    \resitem{Coordinating and confirming change order requests with homeowners.}
    \resitem{Interacting with subcontractors, vendors, and suppliers to procure materials and obtain insurance formwork and Material Safety Data sheets (MSDSs), on a per-project basis to ensure compliance.}

    \resitem{3D modeling and rendering of project designs for client presentations and regulatory approvals.}
    \resitem{Other responsibilities include market research to find potential vendors, suppliers, and subcontractors, looking into potential certifications for Icon, and undertaking miscellaneous office jobs.}
  \end{itemize}
  \pagebreak
\item
  \ressubheading{LEED Project Experience}{Marin, CA, USA}{Green Building Consultant}{May 2010 - Jun. 2010}
  \begin{itemize}
    \resitem{Working on the SGS Office Buildout, a commercial interior project in its design phase, that is registered with LEED v2.0.}
    \resitem{Involved in the credit calculations, analysis of energy model reports, evaluation of credit costs, troubleshooting of potential setbacks, reviewing documentation for compliance, and drafting Credit Interpretation Requests (CIR).}
  \end{itemize}

\item
  \ressubheading{Cascadia Region Green Building Council}{Seattle, WA, USA}{Intern}{Oct. 2009 - Dec. 2009}
  \begin{itemize}
    \resitem{Involved in marketing and registration promotion for Green Broker Conference organized by Cascadia Region Green Building Council and Commercial Brokers Association.}
    \resitem{Involved in the Program Task Force work for Living Future 2010 along with making calls for session promotion.}
  \end{itemize}
\item
  \ressubheading{Kamal S. Malik}{Mumbai, Maharashtra, India}{Architect Intern}{Jul. 2006 - Nov. 2006}
  \begin{itemize}
    \resitem{Worked on conceptual drawings (perspective and 3D computer models), working drawings, detailing, and involved with client interaction.}
  \end{itemize}
  
\end{itemize}

\resheading{Other Experience}
\begin{itemize}

\item
  \ressubheading{Department of Construction Management, University of Washington}{Seattle, WA, USA}{Research Assistant}{Jun. 2009 - Dec. 2009}
  \begin{itemize}
    \resitem{Worked with Professors Yong-Woo Kim and Ken-Yu Lin to help define an alternative and more efficient green product purchasing methodology.}
    \resitem{Surveyed and compiled the current green procurement practices to get a clear understanding of the current practices.}
    \resitem{Worked closely with SENSEable City Lab, MIT on the Trash Track Project deployment in Seattle, and compiled a report.}
    \resitem{Researched current construction safety issues.}
    \resitem{Worked on 3DS Max models for use in a construction gaming environment software (Torque).}
  \end{itemize}

\item
  \ressubheading{Department of Statistics, University of Washington}{Seattle, WA, USA}{Teaching Assistant}{Sep. 2008 - Jun. 2009}
  \begin{itemize}
    \resitem{Taught students elementary concepts of probability and sampling, binomial and normal distributions, basic concepts of hypothesis testing, estimation, and confidence intervals, t-tests and chi-square tests, through quiz sections and regular office hours.}
  \end{itemize}

\end{itemize}

\resheading{References}
\begin{itemize}
\item \textit{Available on request.}
\end{itemize}
%% \resheading{Other Work Experience}
%% \begin{itemize}

%% \item
%%    \ressubheading{Department of Statistics, University of Washington}{Seattle, WA, USA}{Office Assistant}{Jul. 2009 - Aug. 2009}
%%   \begin{itemize}
%%     \resitem{Data entry for graduating students and the Statistics Tutor Center.}
%%     \resitem{Assisted staff with Microsoft Excel jobs.}
%%     \resitem{Prepared announcement flyers and updated the department's website.}
%%    \end{itemize}

%% \item
%%   \ressubheading{Department of Statistics, University of Washington}{Seattle, WA, USA}{Teaching Assistant}{Sep. 2008 - Jun. 2009}
%%   \begin{itemize}
%%     \resitem{Taught students elementary concepts of probability and sampling, binomial and normal distributions, basic concepts of hypothesis testing, estimation, and confidence intervals, t-tests and chi-square tests, through quiz sections and regular office hours.}
%%   \end{itemize}

%% \end{itemize}

%% \resheading{Noteworthy Academic Projects}
%% \begin{itemize}
%%   \resitem{Application and analysis of the Bachelor Enlisted Quarters, Everett, Washington in terms of LEED rating and certification with recommendations to achieve Gold and Platinum Certification.}
%%   \resitem{Designed a dormitory for North Idaho College as part of the Design Build team for the Design Build course.}
%%     \pagebreak
%%   \resitem{Chalked out a business plan for a commercial contractor for the Business Management course.}
%%   \resitem{Analyzed a Public Private Partnership (P3) Project: Kicking Horse Canyon, Phase 2, BC, Canada.}
%%   \resitem{Analyzed the procurement method for the Benjamin Hall Interdisciplinary Research Building, Seattle, WA, USA.}
%%   \resitem{Worked on a proposal of redesigning the Delhi International Airport, New Delhi, India.}
%%   \resitem{Modified the highway bus stop and street layout of Brahmavar, Karnataka, India to minimize traffic jams.}
%% \end{itemize}

%% \resheading{Relevant Coursework}
%% { \phantom{.} \vspace{3pt} }

%% \begin{spacing}{1.1}
%% \begin{tabular*}{6.5in}{@{\hspace{0.23in}}l @{\extracolsep{\fill}} l}
%% \textbullet\hspace{0.05in} Sustainable Construction &  \textbullet\hspace{0.05in} Design Build \\
%% \textbullet\hspace{0.05in} Principles of Project Management & \textbullet\hspace{0.05in} Advanced Project Management: BIM \\
%% \textbullet\hspace{0.05in} Construction Procurement Systems & \textbullet\hspace{0.05in} Construction Business Management \\
%% \textbullet\hspace{0.05in} Project Economics and Risk Analysis & \textbullet\hspace{0.05in} Construction Law \\
%% \textbullet\hspace{0.05in} Leadership in Construction & \textbullet\hspace{0.05in} Research in Construction \\
%% \textbullet\hspace{0.05in} Building Estimation & \textbullet\hspace{0.05in} Construction Scheduling \\
%% \textbullet\hspace{0.05in} Materials Strengths & \textbullet\hspace{0.05in} Managing International Projects \\
%% \textbullet\hspace{0.05in} Surveying and Leveling & \textbullet\hspace{0.05in} Theory and Analysis of Structures \\
%% \end{tabular*}
%% \end{spacing}
%% { \phantom{.} \vspace{3pt} }

\end{document}
